Bricking up backdoors in Intrusion Detection Systems

### 2019-09-10 ex2/paper/paper.tex
Tiny modification for fine-tuning

\subsection{Neural Network Fine-Tuning}
%\todo{Max: It said pruning before but should be tuning, right?}
%AH. I guess both should work
\begin{figure}[t]
%\includegraphics[width=\columnwidth]{figures/finetuning_2015.pdf}
\includegraphics[width=\columnwidth]{figures/finetuning_2017.pdf}
\caption{Fine-tuning of the \glspl{mui} for \unsw{}.}
\label{fig:finetuning}
\end{figure}
In addition to pruning, we tried to use fine-tuning to remove the backdoor from the \gls{mlp} classifier.
The use of fine-tuning exclusively makes  sense if both the computational effort and the required training set size for fine-tuning are substantially lower than for the original training procedure.

\autoref{fig:finetuning} shows the backdoor efficacy when continuing training of our trained model for both \unsw{} and \cic{} with the validation set, hence without backdoored samples.
It indicates clearly that, unfortunately, with reasonable computational effort, fine-tuning is uneffective for cleaning the \gls{mui} from backdoors in our case. In fact, training a model from scratch takes less computational effort than fine-tuning.

>>>>

\subsection{Neural Network Fine-Tuning}
%\todo{Max: It said pruning before but should be tuning, right?}
%AH. I guess both should work
\begin{figure}[t]
%\includegraphics[width=\columnwidth]{figures/finetuning_2015.pdf}
\includegraphics[width=\columnwidth]{figures/finetuning_2017.pdf}
\caption{Fine-tuning of the \gls{mui} for \unsw{}.}
\label{fig:finetuning}
\end{figure}
In addition to pruning, we tried to use fine-tuning to remove the backdoor from the \gls{mlp} classifier.
The use of fine-tuning exclusively makes  sense if both the computational effort and the required training set size for fine-tuning are substantially lower than for the original training procedure.

\autoref{fig:finetuning} shows the backdoor efficacy when continuing training of our trained model for \cic{} with the validation set, hence without backdoored samples.
It indicates clearly that, unfortunately, with reasonable computational effort, fine-tuning is uneffective for cleaning the \gls{mui} from backdoors in our case. In fact, training a model from scratch takes less computational effort than fine-tuning. We observed a similar behaviour for \unsw{}.
